Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-09-13 manuscript/manuscript.tex
minor changes

The underlying software stack for running the tutorial consists of:
\begin{itemize}
\item \textbf{PyEMMA} -- MSM/HMM estimation, validation, analysis, and visualization, and its dependencies~\cite{pyemma}
\item mdshare -- A downloader for MD data from a public server
\item notebook -- The Jupyter~\cite{jupyter} notebook tool used for running the tutorials, along with extension packages jupyter\-\_contrib\_nbextensions and nbexamples
\item matplotlib -- A plotting library~\cite{matplotlib}
\item nglview -- Widget for active viewing of molecular structures in Jupyter environments~\cite{nglview}
\end{itemize}

@@

For a more detailed description of author contributions, see the GitHub issue tracking and changelog at\\\githubrepository{}.

>>>>

The underlying software stack for running the tutorial consists of:
\begin{itemize}
\item \textbf{PyEMMA} -- MSM/HMM estimation, validation, analysis, and visualization, and its dependencies~\cite{pyemma}
\item mdshare -- A downloader for MD data from a public server
\item notebook -- The Jupyter~\cite{jupyter} notebook tool used for running the tutorials, along with extension packages jupyter\_contrib\_nbextensions and nbexamples
\item matplotlib -- A plotting library~\cite{matplotlib}
\item nglview -- Widget for active viewing of molecular structures in Jupyter environments~\cite{nglview}
\end{itemize}

@@

For a more detailed description of author contributions, see the GitHub issue tracking and changelog at \githubrepository{}.
